Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-06-22 Paper/paper.tex
start of s4

\includegraphics[width=0.65\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.65\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.65\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr30}

@@

In the previous section we showed that we begin to care for the effects of NS's
deformation due to its companion hole's tidal field, if (a) the BH is sufficiently
small, (b) BH spin is aligned and $\gtrsim +0.4$, and (c) the NS is
not very compact, with $\lambdans\gtrsim 1000$. The first two conditions
enhance tidal effects on emitted GWs by increasing the number of orbits at small
separation, where the deviation of NSBH and BHBH dynamics is the largest. The third,
i.e. (c), simply makes the NS more easily deformable. All of them reduce the onset 
frequency for NS's disruption close to merger. Therefore, systems that fulfill the 
above conditions have considerably (or, at least, the most) different GW morphology
when compared to equivalent BHBH coalescences. Ultimately, the extent of 
tidal modulations of emitted GWs depends on the equation of state of neutron star
matter, which becomes an indirect measurable in GW astrophysics.
% 
However, if we do indeed receive GWs from such a binary source, what information can we
possibly extract from it about the internal structure of neutron stars?
In this section we consider this question in perspective of measuring the tidal 
deformability parameter of neutron stars purely from gravitational waves they emits 
while orbiting spinning black holes.
%

>>>>

\includegraphics[width=0.62\columnwidth]{plots/McEta2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.62\columnwidth]{plots/EtaChiBH2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.62\columnwidth]{plots/McChiBH2D_q4_mc2_25_chi0_50_snr30}\\
\includegraphics[width=0.62\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.62\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr30}
\includegraphics[width=0.62\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr30}\\
\includegraphics[width=0.6\columnwidth]{plots/LambdaMc2D_q4_mc2_25_chi0_50_snr50}
\includegraphics[width=0.6\columnwidth]{plots/LambdaEta2D_q4_mc2_25_chi0_50_snr50}
\includegraphics[width=0.6\columnwidth]{plots/LambdaChiBH2D_q4_mc2_25_chi0_50_snr50}

@@

In the previous section, we showed that the effects of NS's deformation due to
its companion hole's tidal field becomes discernible in GW spectrum only when
the following hold: (a) the BH has a sufficiently small mass, (b) BH spin
is positive aligned, i.e. $\chibh\gtrsim +0.4$, (c) the NS is not very compact,
with $\lambdans\gtrsim 1000$, and finally, (d) the source is close enough
such that SNR $\gtrsim 30$.
% 
The first two conditions both enhance the tidal distortion of the star and increase
the number of orbits the system goes through at small separation, where the
differences between NSBH and BHBH signals is maximal.
% 
The third simply makes the NS more easily deformable. All of them also reduce
the onset frequency of NS's disruption, allowing for it to happen earlier in
the orbit. 
% 
In addition, a SNR of $30$ corresponds to a $1.35+5M_\odot$ binary with 
$\chibh = 0.4$ at a luminosity distance of $XXX$~Mpc, if optimally aligned
with LIGO. If, instead, it subtends a non-zero angle with LIGO's line of sight
(say $45^o$), the binary would need to be at $\approx XXX$~Mpc to achieve the
same signal strength.

Ultimately, the extent of tidal modulations of emitted GWs depends on the
equation of state of neutron star interior, which becomes an indirect
measurable in GW astrophysics.
% 
We therefore turn to the question: If we do observe GWs from disruptive 
coalescing NSBHs, what information can we extract from them about the internal
structure of neutron stars?
% 
We calculate here the accuracy with which we measure $\lambdans$ from a 
{\it single} GW observation. We will focus on combining multiple observations
in the following section.
